\cvsection{Profile}
I'm a person that seeks out opportunities to further my knowledge about the world.
I enjoy the process of figuring out how things work. In my professional life,
this translates to a willingness to take up tasks that I have not done before.
Inspired by my mentors I try to embrace the idea of extreme ownership and put it to work in my day-to-day efforts.

\cvsection{Skills}
%\smallskip
\begin{itemize}
\item My primary skills are \textbf{Node.js} and \textbf{JavaScript}. I worked with many popular npm libraries e.g. Jest and Mocha for testing, or \textbf{Express} and \textbf{Hapi} for building REST APIs.
\item To a lesser extend I’m experienced with \textbf{Docker}, \textbf{Kubernetes}, \textbf{Nginx}, \textbf{Python}, \textbf{MongoDB}, \textbf{SQL}, \textbf{Bash}, Apollo Server, and popular front-end frameworks such as \textbf{React} or \textbf{Vue}.
\item I’m proficient with \textbf{Git} and \textbf{Subversion} and used to working with \textbf{Jira} and \textbf{Confluence}.
\item I’m familiar with popular \textbf{UNIX} based systems — \textbf{Linux} and MacOs.
\end{itemize}

\cvsection{Education}
\cvevent{The Silesian University of Technology}{Bachelor of Engineering,\\ Automatic Control and Robotics}{2015 -- 2019}{Gliwice, Poland}
\begin{itemize}
    \item In the course of writing my final thesis, I employed Python and Tensorflow to study the benefits of using neural nets in data analysis.
    \item As a part of my assignments, I created several small projects using Python, Node.js, Matlab, and C++.
    \item I received scholarship for the best students.
\end{itemize}

\cvsection{Languages}
\begin{itemize}
    \item Polish (native)
    \item English (C1, professional proficiency)
\end{itemize}
